Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-19 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

Even if $\iota$ is not a THOS rule, the composited function~$\iota\circ\mu$
may still be a QIVPM under so suitable conditions. For example, Eq.~(\ref{eq:iota-Inclusion})
can be weaken as follow: for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
their sum~$x_{0}+x_{1}\in\left[0,1\right]$ implies
\begin{equation}
\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),$\iota\circ\mu$
still must be a QIVPM~\citep{HOSTunpublished}.

>>>>

Even if $\iota$ is not a THOS rule, the composited function~$\iota\circ\mu$
may still be a QIVPM under some suitable conditions. For example,
Eq.~(\ref{eq:iota-Inclusion}) can be weaken as follow: for any numbers~$x_{0}$
and $x_{1}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}\in\left[0,1\right]$
implies
\begin{equation}
\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
Then, given a Hilbert space of dimension~$d\le3$, when $\iota$
satisfies Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add}),
$\iota\circ\mu$ still must be a QIVPM~\citep{HOSTunpublished}.
